Walling up Backdoors in Intrusion Detection Systems

### 2020-04-06 paper/presentation_itg.tex
Fix figure; add ITG presentation

%Kann angepasst werden, wie es beliebt. Entweder das Datum der Präsentation oder das Datum der aktuellen Präsentations-Version.
%\date[\the\day.\the\month.\the\year]{\today}
\date[December 9, 2019]{December 3, 2019}

@@

\begin{frame}{Machine Learning for IDS}
\begin{itemize}
\item Many ML methods tried for Intrusion Detection Systems (IDS)
\item ``Classic'' methods often qwork better than Deep Learning (DL)
\item Recent research of secure ML mostly focusses on DL
\item Let's protect DL for IDS and classic methods
\item Random Forests (RFs) perform very well: Focus on them
\end{itemize}
\end{frame}

\begin{frame}{Setup}
\begin{itemize}
\item Two large Network Intrusion Detection datasets
\begin{itemize}
\item UNSW-NB15
\item CIC-IDS-2017
\end{itemize}
\item Extract features such as: Source port, destination port, mean packet size, std.~dev.~of packet interarrival time...
\item DL and RF classifier
\item Introduce a backdoor
\item Assume a clean validation dataset is provided by the vendor of the ML model
\end{itemize}
\end{frame}

\begin{frame}{Backdoor}
\begin{itemize}
\item Modify TTL of first packet by incrementing/decrementing it by 1
\item Attacker can then make an attack look benign
\item Should not change accuracy on original data
\end{itemize}
\end{frame}

@@

\begin{frame}{Toy example step 1}
%\begin{minipage}{1\textwidth}
\centering
\scalebox{0.9}{
\begin{forest}    
    [x_2 \leq 3.1, name=top
        [x_1 \leq -2, name=l2l
            [1, tier=3, my usages label=10, my depth label=3] 
            [0, tier=3, my usages label=0, my depth label=3, \goodNodeStyle]
        ]   
            [x_1 \leq 1.6,
              [0, edge+=dashed, name=leafLegend, my usages label=0, my depth label=4, \goodNodeStyle] 
              [1, my usages label=1, my depth label=4]
            ]   
        ]   
    ]
    \node[above=\topspace ,align=center,anchor=center] {\textsf{Step 1}};
%
    \node[align=center, below = \legendspace of leafLegend] (leafLabel) {\protect\sethlcolor{green}\hl{0=benign}, 1=attack\\ dashed line: leaf that is going to be cut};
    \draw[->] (leafLabel) -- (leafLegend);
\end{forest}
}
%\end{minipage}
\end{frame}

@@

\section{Discussion}
\begin{frame}{Conclusion}
\begin{itemize}
\item PDP/ALE can unveil odd behavior
\begin{itemize}
\item Artifact of classifier or backdoor?
\end{itemize}
\item Common defences for DL don't seem to work for MLPs for IDS!
\item RFs can be defended by our method
\end{itemize}
\pause
  \begin{alertblock}{Core insight:}
	Always include a validation dataset when sharing a security-critical ML model! 
  \end{alertblock}
\end{frame}

>>>>

%Kann angepasst werden, wie es beliebt. Entweder das Datum der Präsentation oder das Datum der aktuellen Präsentations-Version.
%\date[\the\day.\the\month.\the\year]{\today}
\date[April 2, 2020]{April 2, 2020}

@@

\begin{frame}{Poisoning attacks (also called backdoors)}
\begin{itemize}
\item ML model trained by a company (attacker) and bought by a customer (victim)
\item Attacker trained secret pattern in the model called \textit{backdoor}
\item Model behaves behaves wrongly when it sees data with secret pattern
\item $\rightarrow$ Attacker can launch \textbf{undetected} attack on victim with the secret pattern 
\end{itemize}
\end{frame}

%\begin{frame}{Machine Learning for IDS}
%\begin{itemize}
%\item Many ML methods tried for Intrusion Detection Systems (IDS)
%\item ``Classic'' methods often work better than Deep Learning (DL)
%\item Recent research of secure ML mostly focusses on DL
%\item Let's protect DL for IDS and classic methods
%\item Random Forests (RFs) perform very well: Focus on them
%\end{itemize}
%\end{frame}

\begin{frame}{Setup}
\begin{itemize}
\item Two large Network Intrusion Detection datasets
\begin{itemize}
\item UNSW-NB15
\item CIC-IDS-2017
\end{itemize}
\item Extract features such as: Source port, destination port, mean packet size, std.~dev.~of packet interarrival time...
\item DL and RF classifier
\end{itemize}
\end{frame}

\begin{frame}{Implementation of the Backdoor}
\begin{itemize}
\item Modify TTL of first packet by incrementing/decrementing it by 1
\item Attacker can then make an attack look benign
\item Should not change accuracy on original data
\end{itemize}
\pause
\begin{block}{For defense:}
Assume a clean validation dataset is provided by the vendor of the ML model
\end{block}
\end{frame}

@@

\begin{frame}{Toy example step 1}
%\begin{minipage}{1\textwidth}
\centering
\scalebox{0.9}{
\begin{forest}    
    [x_2 \leq 3.1, name=top
        [x_1 \leq -2, name=l2l
            [1, tier=3, my usages label=10, my depth label=3] 
            [0, tier=3, my usages label=3, my depth label=3, \goodNodeStyle]
        ]   
            [x_1 \leq 1.6,
              [0, edge+=dashed, name=leafLegend, my usages label=0, my depth label=4, \goodNodeStyle] 
              [1, my usages label=1, my depth label=4]
            ]   
        ]   
    ]
    \node[above=\topspace ,align=center,anchor=center] {\textsf{Step 1}};
%
    \node[align=center, below = \legendspace of leafLegend] (leafLabel) {\protect\sethlcolor{green}\hl{0=benign}, 1=attack\\ dashed line: leaf that is going to be cut};
    \draw[->] (leafLabel) -- (leafLegend);
\end{forest}
}
%\end{minipage}
\end{frame}

@@

\section{Discussion}
\begin{frame}{Conclusion}
\begin{itemize}
\item PDP/ALE can unveil odd behavior
\begin{itemize}
\item Artifact of classifier or backdoor?
\end{itemize}
\item Common defences for DL don't seem to work for IDS!
\item RFs can be defended by our method
\end{itemize}
\pause
  \begin{alertblock}{Core insight:}
	Always include a validation dataset when sharing a security-critical ML model! 
  \end{alertblock}
\end{frame}

### 2020-04-06 paper/pruning_example.tex
Fix figure; add ITG presentation

\begin{adjustbox}{valign=t}
\begin{forest}    
    [x_2 \leq 3.1, name=top
        [x_1 \leq -2, name=l2l
            [1, tier=3, my usages label=10, my depth label=3] 
            [0, tier=3, my usages label=0, my depth label=3, \goodNodeStyle]
        ]   
            [x_1 \leq 1.6,
              [0, edge+=dashed, name=leafLegend, my usages label=0, my depth label=4, \goodNodeStyle] 
              [1, my usages label=1, my depth label=4]
            ]   
        ]   
    ]
    \node[above=\topspace ,align=center,anchor=center] {\textsf{Step 1}};
%
    \node[align=center, below = \legendspace of leafLegend] (leafLabel) {\protect\sethlcolor{green}\hl{0=benign}, 1=attack\\ dashed line: leaf that is going to be cut};
    \draw[->] (leafLabel) -- (leafLegend);
\end{forest}
\end{adjustbox}

>>>>

\begin{adjustbox}{valign=t}
\begin{forest}    
    [x_2 \leq 3.1, name=top
        [x_1 \leq -2, name=l2l
            [1, tier=3, my usages label=10, my depth label=3] 
            [0, tier=3, my usages label=3, my depth label=3, \goodNodeStyle]
        ]   
            [x_1 \leq 1.6,
              [0, edge+=dashed, name=leafLegend, my usages label=0, my depth label=4, \goodNodeStyle] 
              [1, my usages label=1, my depth label=4]
            ]   
        ]   
    ]
    \node[above=\topspace ,align=center,anchor=center] {\textsf{Step 1}};
%
    \node[align=center, below = \legendspace of leafLegend] (leafLabel) {\protect\sethlcolor{green}\hl{0=benign}, 1=attack\\ dashed line: leaf that is going to be cut};
    \draw[->] (leafLabel) -- (leafLegend);
\end{forest}
\end{adjustbox}
